R Notebook

### 2020-12-22 AdvendOfCode2020/day09.Rmd
Day 11 puzzle 1

@@

@@

# Now we must find a continuous range of falues which the sum is equal
# the value found in step 1

# Calc all possible "continuous" range index
rangeComb <- combn(1:length(input),2)

@@

>>>>

#### Solution

The solutions is pretty straighforward, we use the preamble as a _slide window_ along the transmission data and do a combination of two from the preamble and sum it, so we check if the next number is one of the possible value from it.

@@

#### Solution

We'll apply the same idea from part 1, to find which value is invalid. After that we create a array of continuous values from one to size of transmission, combine then, sum and find which ones are equal to the invalid value found.

@@

# Now we must find a continuous range of values which the sum is equal
# the value found in step 1

# Calculates all possible "continuous" range index
rangeComb <- combn(1:length(input),2)

@@

There is it!

### 2020-12-22 AdvendOfCode2020/day_08.Rmd
Day 11 puzzle 1

@@

@@

executeProgram <- function(.program, acc=0, ptr=1, canChange=F){

@@

```

>>>>

#### Solution

This is fun remembers me my old assembly classes in the college.

We'll create a function to decode the input text in to a data frame of commands and arguments and a execution counter, to check if that command was already executed and so detect a loop. And we'll _run_ the data frame processing each command (row) until the end it or to find a loop. We update the execution counter for each row executed.

@@

#### Solution

We'll use the same idea to part one, but here let's put the code that _runs_ a program (the code data frame) in a more sophisticated function. This function will returns if a program ended if with a error (jump to a invalid position), with a loop (executed the same instruction twice) or with success (run the last command).

To find which command we need to change, we just find with positions of instructions `nop` or `jmp` in the original code, and for each one, change it, run the changed program and check the outcome, until we find a programa that works.

@@

# Emulates the execution of a code returning:  
# ERROR if the execution jumps to a invalid position
# LOOP, if executes the same instruction twice
# END if run the last command nicelly
executeProgram <- function(.program, acc=0, ptr=1, canChange=F){

@@

```
That is our response.
